---
title: "p8105_hw3_cx2227"
author: "Chuyue Xiang"
date: "10/10/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggridges)
```

## Problem 1

```{r, results='hide'}
library(p8105.datasets)
data("instacart")

str(instacart)
```

### Short description 
- The `instacart` dataset has 1384617 observations and 15 variables.
- There are 4 character variables and 11 numeric variables.
- This dataset contains data of various products.
- Some of the key variables are order_id, product_id, aisle_id, and days_since_prior_order.
- For example, Bulgarian Yogurt with prouct id 49302 has been reordered once 9 days since the prior order.


### Part 1: How many aisles are there, and which aisles are the most items ordered from?


```{r,results='hide'}
instacart %>% 
  group_by(aisle) %>% 
  summarize(n_obs = n()) %>%
  arrange(desc(n_obs)) 
```
- There are 134 aisles.
- The "fresh vegetables" aisle has the most items.

### Part 2: Make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered. Arrange aisles sensibly, and organize your plot so others can read it.

```{r, fig.width=8}
instacart %>% 
  group_by(aisle) %>% 
  summarize(n_obs = n()) %>% 
  filter(n_obs > 10000) %>% 
  arrange(aisle) %>% 
  
  ggplot(aes(x = aisle, y = n_obs)) + geom_bar(stat = "identity") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  scale_y_continuous(breaks = seq(10000,160000,5000)) + 
  labs(x = "Aisle names", y = "Number of items ordered") +
  geom_text(aes(label=n_obs), vjust=-0.3, size=2.5)
```

- The number if items ordered from aisle "fresh fruits" and "fresh vegetables" are way more than others, followed by "packaged vegetables fruits" and "yogurt".



### Part 3: Make a table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”. Include the number of times each item is ordered in your table.

```{r}
instacart %>% 
  filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>% 
  group_by(aisle, product_name) %>% 
  summarize(tot_order = sum(order_number)) %>% 
  mutate(ord_ranking = min_rank(desc(tot_order))) %>% 
  filter(ord_ranking %in% c(1,2,3)) %>% 
  arrange(aisle, ord_ranking) %>% 
  knitr::kable()
```
 
 
 - The most popular item in baking ingredients are Light Brown sugar, Cane sugar, and Organix Vanilla Extract.
 - The most popular item in dog food care are standard size pet waste bags, beef stew canned dog foo, and snack sticks Chicken & Rice Recipe Dog Treats.
 - The most popular item in packagedd vegetables fruits are organic baby spinach, organix raspberries, and organix blueberries.


### Part 4: Make a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week; format this table for human readers (i.e. produce a 2 x 7 table).

```{r}
instacart %>% 
  filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>% 
  group_by(product_name, order_dow) %>% 
  summarize(mean_order_hour_of_day = mean(order_hour_of_day)) %>% 
  pivot_wider(names_from = order_dow, values_from = mean_order_hour_of_day) %>% 
  knitr::kable()
```


 - Purchases are mainly occured on afternoons for both products.



## Problem 2

```{r,results='hide'}
library(p8105.datasets)
data("brfss_smart2010")
```

### Part 1: Data cleaning

```{r}
brfss_smart2010 = brfss_smart2010 %>% 
  janitor::clean_names() %>% 
  filter(topic == "Overall Health", response %in% c("Excellent", "Very good", "Good", "Fair","Poor")) %>%   
  mutate(response = fct_relevel(response, "Poor", "Fair", "Good", "Very good","Excellent")) 

brfss_smart2010
```

### Part 2: In 2002, which states were observed at 7 or more locations? What about in 2010?

```{r}
brfss_smart2010 %>% 
  filter(year == 2002) %>% 
  group_by(locationabbr, locationdesc) %>% 
  summarize(n_obs = n()) %>% 
  group_by(locationabbr) %>% 
  summarize(n_obs = n()) %>% 
  filter(n_obs >= 7)
```


```{r}
brfss_smart2010 %>% 
  filter(year == 2010) %>% 
  group_by(locationabbr, locationdesc) %>% 
  summarize(n_obs = n()) %>% 
  group_by(locationabbr) %>% 
  summarize(n_obs = n()) %>% 
  filter(n_obs >= 7)
```

 - In 2002, CT, FL, MA, NC, HJ, PA were observed at 7 or more locations.
 - In 2010, CA, CO, FFL, MA, MD, NC, NE, NJ, NY, OH, PA, SC, TX, WA were observed at 7 or mroe locations.


### Part 3: Construct a dataset that is limited to Excellent responses, and contains, year, state, and a variable that averages the data_value across locations within a state. Make a “spaghetti” plot of this average value over time within a state 

```{r}
brfss_smart2010 %>% 
  filter(response == "Excellent") %>% 
  group_by(year, locationabbr, locationdesc) %>% 
  summarize(avg_data_value = mean(data_value)) %>% 
  select(year, locationabbr, locationdesc, avg_data_value) %>% 
  ggplot(aes(x = year, y = avg_data_value)) + 
   geom_line(aes(group = locationabbr)) + 
   labs(x = "Year", y = "Average Data Value") 
```

 - a spaghetti plot might not be the best choice in this situation
 
 
### Part 4: Make a two-panel plot showing, for the years 2006, and 2010, distribution of data_value for responses (“Poor” to “Excellent”) among locations in NY State.
 
```{r}
plot2006 = brfss_smart2010 %>% 
  filter(year == 2006, response %in% c("Excellent", "Very good", "Good", "Fair","Poor"), locationabbr == "NY") %>% 
  ggplot(aes(x = response, y = data_value)) + 
  geom_boxplot() +
  labs(x = "Response", y = "Data Value", title = "2006") 

plot2006
```

```{r}
plot2010 = brfss_smart2010 %>% 
  filter(year == 2010, response %in% c("Excellent", "Very good", "Good", "Fair","Poor"), locationabbr == "NY") %>% 
  ggplot(aes(x = response, y = data_value)) + 
  geom_boxplot() +
  labs(x = "Response", y = "Data Value", title = "2010")

plot2010
```

 - The distribution of data_value in response did not change a lot from 2006 to 2010.